\documentclass{article}
\usepackage{graphicx}
\usepackage[T1]{fontenc}

\begin{document}
	
	\title{}
	\author{Nico Limacher}
	
\maketitle

\section{Important Changes From 3 to 4}

	\begin{itemize}
		\item New tool: Flexbox. To be discussed later.
		\item Main unit used switched from px to rem.
		\item The global font size is by default now 16.
		\item Now includes a fifth screen-size.
		\item New utility classes.
		\item New JS library that needs to be included.
	\end{itemize}

\section{Setting up Bootstrap 4}

	Aforementioned new library: just use a CDN to include. JS libraries \emph{need to be in order}
	
	\begin{enumerate}
		\item jquery
		\item popper - deals with dropdowns and pop-ups
		\item base bootstrap JS files
	\end{enumerate}
	
	\paragraph*{Starter Template} Like an HTML boilerplate, but includes Bootstrap as well. Just google for it

\section{Colors and Backgrounds}

	\paragraph*{Contextual Color Classes} Things like "Danger", "Warning". Not explicit colors but have meaning attached. Have default values that changed in 4. New classes added "Secondary", "Dark" etc.
	
\section{Typography}

	\begin{itemize}
		\item Page Headings
		\\Obviously have h1,h2... still but can also use "display-1", "display-2" etc. as classes
		\item Block Quotes
		\\Using class="blockquote" or class="blockquote text-right"
		\item Pixels to Rems
		\\A.k.a. Root-ems, a relative unit to the default browser pixel size
		\\This is good because things scale together
	\end{itemize}

\section{New Fancy Spacing Utilities}

	Things like shadows, alignment, margin, padding etc.
	
	\begin{enumerate}
	\item Class: border (further adjust like border-top, border-primary)
	\\By default a thin, light gray border
	\item Class: m, p (m- margin, p- padding)
	\\Pick location with t- top, x- both left and right, b- bottom etc...
	\\Then pick size with 0-5 or Auto, based on rem.
	\end{enumerate}	

\section{Responsive Breakpoints}

	New Screensizes (XS, S, M, L, XL)
	\\Can selectively pad and margin based on screen size
	\\Like specifying for size M \emph{and above} for M

\section{New Navbars}
	
	\begin{itemize}
		\item Can now decide when we want the bar to expand/contract
		\item Now have control of background color
	\end{itemize}

\section{New Display Utility}

	For hidden/visible content: now have class d-{value}
	Ex:
	\begin{verbatim}
	class="d-xl-none"
	\end{verbatim}
	will hide the object on large screens

\end{document}